---
title: "Bash Tutorial"
subtile: Week 01
author: "Chris Mantegna"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
  theme: cerulean
  highlight: 
    toc: true
    toc_float: true
    number_sections: true
    code_folding: show
    code_download: true
    callout-appearance: default
---

# Must download this file before getting started: https://d.pr/f/BDaGTy. I downloaded from the course page and unzipped, placed in data file for coursework repo.
```{r, engine=bash}

pwd 

```
# unzipped and pulled from local machine. verifying files exist
```{r, engine=bash}

cd ../data/data-shell/data-shell
ls

```
```{r, engine=bash}

whoami

```

```{r, engine=bash}

pwd

```
# Moving back to the directory that has my data file per the exercise directions
```{r, engine=bash}

cd /home/shared/8TB_HDD_02/cnmntgna/GitHub/chris-coursework1/data/data-shell/data-shell
ls

```
# 
```{r, engine=bash}

cd /home/shared/8TB_HDD_02/cnmntgna/GitHub/chris-coursework1/data/data-shell/data-shell
ls -F

```

```{r, engine=bash}

 ls -F data-shell

```
```{r, engine=bash}

 ls -F /data-shell

```
# I've only had success with the full path
```{r, engine=bash}

cd /home/shared/8TB_HDD_02/cnmntgna/GitHub/chris-coursework1/data/data-shell/data-shell
ls -F

```

```{r, engine= bash}

 ls ../data-shell/north-pacific-gyre/2012-07-03/

```

```{r, engine= bash}

 ls /home/shared/8TB_HDD_02/cnmntgna/GitHub/chris-coursework1/data/data-shell/data-shell/north-pacific-gyre/2012-07-03/

```

```{r, engine= bash}

cd ../data/data-shell/data-shell
ls -F

```
```{r, engine= bash}

mkdir thesis

```

```{r, engine= bash}

ls -F
```

```{r, engine= bash}

mv thesis/ ../data/data-shell/data-shell
ls -F

```

```{r, engine= bash}

cd ../data/data-shell/data-shell
ls -F

```

```{r, engine= bash}

cd /thesis

```
# since that wasn't enough path for the computer to follow me, i added this to get to the desired location
```{r, engine= bash}

cd ../data/data-shell/data-shell/thesis
ls

```

```{r, engine= bash}

cd ../data/data-shell/data-shell/thesis
nano draft.txt

```







